Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm

### 2024-08-22 paper/main.tex
Added first section of the description of the matlab script

\usepackage{cuted}
\usepackage{stfloats}
\usepackage{tabularray}

@@

\subsection{Simulation Parameter Section}
In the Simulation Parameter Section,

>>>>

\usepackage{cuted}
\usepackage{stfloats}
\usepackage{tabularray}
\usepackage{matlab-prettifier}

@@

\subsection{Simulation Parameter Section}
In the Simulation Parameter Section, static parameters for the following sections are defined.
These include the sampling frequency $f_{s}$, the duration of the whole simulation, the wanted SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the duration of the Goertzel algorithm segments, and the time that should
be taken into account by the EMA.
By adjusting these parameters, the behavior of the receiver can be altered to, e.g. to simulate different receiving conditions.

\subsection{Signal Creation Section}

\begin{lstlisting}[style=Matlab-editor]
    %Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
    dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;

    %Add noise by passing the DCF77 signal through an AWGN-Channel
    dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
\end{lstlisting}
